%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\setlength{\footskip}{4.08003pt}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{ragged2e}

\usepackage{xcolor}
\hypersetup{colorlinks,urlcolor=blue}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}


% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}


% Adjust margins
% \setlength{\topmargin}{-0.75in}
% \setlength{\textheight}{10.5in}  % Increase the text height
% \setlength{\oddsidemargin}{-0.5in}
% \setlength{\evensidemargin}{-0.5in}
% \setlength{\textwidth}{7in}


\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\hypersetup{%
  colorlinks=true,% hyperlinks will be colored
  linkcolor=blue,% hyperlink text will be green
  linkbordercolor=blue,% hyperlink border will be red
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
\textbf{\Huge \scshape Ayush Patel} \\ \vspace{10pt}

\faGithub \hspace{-0.2pt} \href{https://github.com/ayush2004patel}{\underline{github.com/ayush2004patel}} ~
\faGlobe \hspace{-0.2pt} \href{https://ayushpatel.co/}{\underline{ayushpatel.co}} ~
\faLinkedin \hspace{-0.2pt} \href{https://www.linkedin.com/in/ayush-patel2004/}{\underline{linkedin.com/in/ayush-patel2004}} \\ 
\vspace{10pt} \faPhone \hspace{-0.2pt} \href{tel:7984886601}{\underline{+91 7984886601}} ~
\vspace{10pt} \faEnvelope \hspace{-0.2pt} \href{mailto:ayushpatel2044.work@gmail.com}{\underline{ayushpatel2044.work@gmail.com}}
\end{center}

% ---------- SUMMARY ----------
\section{Summary}
\vspace{6pt}
\resumeSubHeadingListStart
\item
\small{Full-stack developer proficient in the MERN stack, React.js, and Next.js. Passionate about building scalable applications and solving complex problems.}
\resumeSubHeadingListEnd


% ---------- EDUCATION ----------

\section{Education} \vspace{5pt}
\resumeSubHeadingListStart
\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    {\large Swarrnim Startup and Innovation University} & {\large Ahmedabad, Gujarat, India} \\
    \small Bachelor of Technology in Computer Engineering & \small Current SGPA: 9.40/10
\end{tabular*}
\resumeSubHeadingListEnd



% ---------- PROJECTS ----------

\section{Projects}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/ayush2004patel/collaborative-editor}{LiveDocs}\hspace{5pt}}{{[Next.js, TypeScript, Liveblocks, Lexical Editor, Tailwind CSS]}}}{}
\resumeItemListStart
\resumeItem{Developed a real-time collaborative text editor focused on simplifying document collaboration and boosting productivity through seamless multi-user editing.}
\resumeItem{Implemented document management features, including create, delete, and share, for efficient workflow.}
\resumeItem{Enhanced user experience with inline comments, presence indicators, and activity notifications for seamless communication.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/ayush2004patel/social_media_app}{Postgram}\hspace{5pt}}{{[React.js, Appwrite, React Query, TypeScript, Shadcn, Tailwind CSS]}}}{}
\resumeItemListStart
\resumeItem{Built a responsive social media platform with features for exploring, liking, and saving posts, plus a detailed post view.}
\resumeItem{Developed user-friendly profile and post management, including create, edit, and drag-and-drop file functionality.}
\resumeItem{Utilized Appwrite for backend services and React Query for efficient data fetching and caching.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/ayush2004patel/Portfolio-v2}{Portfolio}\hspace{5pt}}{{[React.js, Three.js, React Three Fiber, React Three Drei, Email JS, Tailwind CSS]}}}{}
\resumeItemListStart
\resumeItem{Developed an immersive 3D portfolio website using React.js, React Three Fiber, and Three.js, creating a unique and engaging user experience.}
\resumeItem{Implemented interactive features such as a dynamic project showcase and animated timeline.}
\resumeItem{Integrated email functionality using EmailJS, enabling visitors to easily contact you through the website.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeProjectHeading
{\textbf{\href{https://github.com/ayush2004patel/prod-store}{ProdStore}\hspace{5pt}}{{[React.js, Node.js, Express.js, MongoDB, Chakra UI]}}}{}
\resumeItemListStart
\resumeItem{Developed a responsive product listing website using React.js and Chakra UI, focusing on a clean and user-friendly interface.}
\resumeItem{Implemented full CRUD operations for product management, allowing users to add, update, view, and delete products.}
\resumeItem{Utilized Node.js, Express.js, and MongoDB to build a backend for data storage and retrieval.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\vspace{5pt}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
      \textbf{Languages}{: Java, JavaScript } \\
      \vspace{3pt}\textbf{Libraries/Frameworks}{: React.js,Node.js, Express.js} \\
      \vspace{3pt}\textbf{UI Component Libraries}{: Chakra UI, Shadcn UI, Material UI, Tailwind CSS} \\
      \vspace{3pt}\textbf{Databases/Servers}{: MongoDB, Mongoose, Appwrite} \\
      \vspace{3pt}\textbf{Platforms/Tools}{: Git/GitHub, VS Code, Postman, NPM, Netlify, Vercel }
      }}
\end{itemize}


%-------------------------------------------
\end{document}

